\documentclass{beamer}

\usecolortheme{seahorse}

\title{Labyrinth}
\subtitle{Revenge of the Grid}
\author{Tom Byrne, Sam Sleight, Bertie Wheen}

\begin{document}
\frame{\titlepage}

\begin{frame}
    \frametitle{The Beginning}
    Initial thoughts: \pause
    \begin{itemize}
        \item Focus on speed \pause
            \begin{itemize}
                \item Optimise grid code \pause
                \item Write localisation from scratch \pause
            \end{itemize}
        \item Engineer Sebastian
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{The Grid}
    Use an array instead of an object heavy representaton. \\ \pause
    Write code to convert provided map. \\ \pause
    Adapt search and movement classes.
\end{frame}

\begin{frame}
    \frametitle{Starting Localisation}
    Look at code given in example project \\ \pause
    Create localisation classes from scratch using our grid representation: \pause
    \begin{itemize}
        \item Probability distribution
            \begin{itemize}
                \item Stores probalities as array \pause
                \item Update in-place instead of creating new each time \pause
            \end{itemize}
        \item Basic action model \pause
        \item (Very) basic sensor model \pause
    \end{itemize}
    Tested on computer. Need to get it working on Sebastian.
\end{frame}

\begin{frame}
    \frametitle{Sebastian}
    Added rotating vision sensor in advance. \\ \pause
    Tested action model in grid. \pause
    \begin{itemize}
        \item Worked, albeit quite slowly \pause
        \item But needed babysitting \pause
            \begin{itemize}
                \item Too big to rotate in places \pause
                \item Could not reverse effectively \pause
            \end{itemize}
    \end{itemize}
    Tested sensor model. \pause
    \begin{itemize}
        \item Perfect sensor models don't work in practice \pause
        \item Confusion with cm and mm \pause
        \item Hampered by sensor range \pause
    \end{itemize}
    Time for The Great Rebuild\texttrademark
\end{frame}

\begin{frame}
    \frametitle{Sebastian 2.0}
    Built entirely from scratch \\ \pause
    Focus on smaller frame and central light sensors \\ \pause
    Code all designed to easily accomodate new robots \\ \pause
    BUT: \pause
    \begin{itemize}
        \item Broke. Absolutely. Everything. \pause
        \item Could no longer traverse the grid. \pause
    \end{itemize}
    Spent way too long trying new movement code and values. \\ \pause
    Could either deal with junctions or deal with a line, but never both. \\ \pause
    Time for a last minute second rebuild. \\
\end{frame}

\begin{frame}
    \frametitle{Sebastian 2.5}
    Similar design, but with sensors on front again. \\ \pause
    Grid now worked again! \\ \pause
    Unfortunately much too late to get any serious sensor models working
\end{frame}

\begin{frame}
    \frametitle{Final Code}
    While unlikely to get it working on Sebastian, we wrote the final bits of code. \\ \pause
    Pulling localisation and search together. \\ \pause
    Works successfully using test models! \\ \pause
\end{frame}

\end{document}

